---
title: "Stroke Prediction"
author: "Irishi"
output: html_document
date: "2022-09-29"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Prediction of Stroke in Patients using Random Forest Algorithm
For this project, we are using a dataset from Kaggle to predict the risk of a stroke in patients.The task is to use a training set to learn and use that knowledge to predict the risk in a testing set. Before the prediction we will do an exploratory data analysis to understand more about the data and finally we will use Random forest Algorithm to predict the outcome.

### Loading Libraries
```{r lib,message=FALSE}
library(tidyverse)
library(caret)
library(randomForest)
library(skimr)
library(ggplot2)
```

### Read Data

```{r read}
df_stroke<-read.csv("C:\\Users\\irish\\Downloads\\archive\\healthcare-dataset-stroke-data.csv",stringsAsFactors = TRUE)
```
### Summarize Data
```{r sum}
summary(df_stroke)
glimpse(df_stroke)
```

```{r sk}
skim(df_stroke)
```
### Data Summary
* There are 5110 rows and 12 columns in the data
* 6 Numeric and 6 Character columns
* 1 Row of other value in gender
* There is a value 'N/A' in bmi in 201 rows

### BMI column is in character format. Converting it to numeric
```{r}
df_stroke$bmi<-as.numeric(df_stroke$bmi)
```


### Changing N/A to NA so that R can understand
```{r}
df_stroke$bmi[df_stroke$bmi=="N/A"]=NA
colSums(is.na(df_stroke))
```


### Replacing NAs
Since height and weight are not provided, we cant calculate bmi and replace NAs with it. In this case,the best option is to replace the NA values with the mean

```{r}
df_stroke$bmi[is.na(df_stroke$bmi)]<-mean(df_stroke$bmi)
colSums(is.na(df_stroke))
```

### Only 1 value as other in gender. So it is better to remove it
```{r}
df_stroke<-df_stroke %>% 
  filter(!gender=="Other")
nrow(df_stroke)
```

### Converting all non-numeric variables to factors

```{r}
df_stroke$stroke<- factor(df_stroke$stroke, levels = c(0,1), labels = c("No", "Yes"))

df_stroke$hypertension<-factor(df_stroke$hypertension,levels = c(0,1),labels=c("No","Yes"))

df_stroke$heart_disease<- factor(df_stroke$heart_disease, levels = c(0,1), labels = c("No", "Yes"))
```


### Plots to Visualize

```{r,ECHO=TRUE}
p1<-ggplot(df_stroke,aes(x=gender,fill=gender))+geom_bar()+
  geom_text(aes(label=..count..),stat = "Count", vjust= 1.5)
p1
p2<-ggplot(df_stroke,aes(x="",y=hypertension,fill=hypertension))+geom_bar(stat = "identity")+coord_polar("y")
p2

```



```{r}

```





